---
title: 'RMarkdown:  In Class Assignment'
author: "Emanuel Padilla"
date: "Data 2401"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
---


```{r setup, include=FALSE}
# Everything in this chunk is R code. 
# You are not expected to understand or edit this yet. 
# We will talk about what this does in a later class, with a little preview in part 2.
knitr::opts_chunk$set(echo = TRUE) 
```


Reminders: 

- You do not need to memorize Markdown syntax.
- You are expected to look things up using:
   - RStudio’s Markdown Help
   - Online documentation or examples
- Click Knit as you go to check that your document still renders correctly.
- Commit at the end, but consider committing as you go as well. 



# Part 1: Markdown Practice

**Do not skip reading this instruction** Create a new section at the end of this section named "Your work here". In that section, complete the tasks below:

- Make a *subsection* called Wise Words. 
- Put your favorite quote in a block quote. 
- Add a working, clickable link to a website that provides more information about that quote.
- Make another *subsection* called "I recommend", and add some information about your favorite author or musician: 
  - A _subsubheading_ with the name of the artist or author;    
  - An example of their writing or lyrics (formatted in a *block of text*);   
  - A _list_ of things they have written or performed (remember to use the formatting markup for a list!), with any of the titles/names in bold.
  
# Your work here
## Wise words 
> Little by little you will create big results. [More info about the  quote](https://www.drginacleo.com/post/the-power-of-tiny-habits-why-small-changes-create-big-results) 

## I recommend:
### Bruno Mars
```
Talking to the moon, in hopes you are on the other side talking to me too. 
```

* **Treasure**
* **24k Magic**
* **Locked out of heaven**






# Part 2: Code Chunks

```{r echo = TRUE}
2 + 2
```

Complete the following steps:

- Knit the document and observe what appears in the output.
- Change the chunk option echo=TRUE to echo=FALSE.
- Knit the document again.
- Finally, write 2–3 sentences answering the following questions:
  - What changed between the two outputs?
  - Did the calculation still run when the code was hidden?
  - Why might someone want to hide code in a report?
  - Why might someone want to show code in a report?
  
The changes between the TRUE and FALSE outputs either showed the code or not. The calculation still ran when the code was hidden. Someone might want to hide code if its long or unnecessary. If the code is important then code must be shown.
  
# Part 3: A small R-in-markdown preview

- Create a subsection within this section called About this document.
- Write 2–3 sentences describing what this document is and what it produces.
- Include one value generated by inline R code.

> To include inline code, use this weird little `r 2+2` pattern, putting the code where I have 2+2 (which is code!) 
> You can use the function `Sys.Date()`, which would be added like this `r Sys.Date()` but you can do something else if you want. (Look at the knit html to see what this does.)

## About this document
This document is an Rmarkdown file which helps us read the text and get to the point in collaboration with not R and Markdown. Producing a clean documentation for the code. Compared to other HTML which is dense with more clutter.  Todays date is `r Sys.Date()`

# Submitting Instructions

When you are finished:  

- Knit the document so that it produces an html file.
- Stage, commit, and push:
  - The updated `.rmd` file 
  - The generated `.html` file
- Submit the GitHub link to the assignment on Canvas.
 
